\section{DWM}

\subsection{TBD}

\begin{itemize}
    \item Gap size per tag
    \item Fsignal
\end{itemize}

\begin{longtable}{|c|c|}
    % caption at the top
    \caption{DWM Keybindings} \\

    \hline
    Key & Action \\
    \hline
    \hline

    \endhead
    \label{tab:dwm-keybindings}


    Super + Shift + Return & Toggle scratch pad. \\
    \hline
    Super + b & Toggle bar. \\
    \hline
    Super + j & Focus next window in stack. \\
    \hline
    Super + k & Focus previous window in stack. \\
    \hline
    Super + Alt + j & Move floating window up. \\
    \hline
    Super + Alt + k & Move floating window down. \\
    \hline
    Super + Alt + l & Move floating window right. \\
    \hline
    Super + Alt + h & Move floating window left. \\
    \hline
    Super + Alt + Shift + j & Resize floating window upward. \\
    \hline
    Super + Alt + Shift + k & Resize floating window downward. \\
    \hline
    Super + Alt + Shift + l & Resize floating window rightward. \\
    \hline
    Super + Alt + Shift + h & Resize floating window leftward. \\
    \hline
    Super + Ctrl + Up & Move floating window to the top edge. \\
    \hline
    Super + Ctrl + Down & Move floating window to the bottom edge. \\
    \hline
    Super + Ctrl + Left & Move floating window to the left edge. \\
    \hline
    Super + Ctrl + Right & Move floating window to the right edge. \\
    \hline
    Super + i & Increase the number of windows in master stack. \\
    \hline
    Super + Shift + i & Decrease the number of windows in master stack. \\
    \hline
    Super + h & Increase the size of master stack. \\
    \hline
    Super + l & Decrease the size of master stack. \\
    \hline
    Super + space & Change master window (main window in master stack). \\
    \hline
    Super + Shift + k & Increase the size of focused window. \\
    \hline
    Super + Shift + j & Decrease the size of focused window. \\
    \hline
    Super + Shift + o & Reset the size of focused window. \\
    \hline
    Super + u & Increase gaps. \\
    \hline
    Super + Shift + u & Decrease gaps. \\
    \hline
    Super + Alt + 0 & Toggle gaps \\
    \hline
    Super + o & Reset gaps to default. \\
    \hline
    Super + Ctrl + j & Push up the stack. \\
    \hline
    Super + Ctrl + k & Push down the stack. \\
    \hline
    Super + Tab & Switch to the last tag set. \\
    \hline
    Super + c & Kill window. \\
    \hline
    Alt + Tab & Cycle through tags. \\
    \hline
    Alt + Shift + Tab & Inverse cycle through tags. \\
    \hline
    Super + t & Tiled layout. \\
    \hline
    Super + f & Floating layout. \\
    \hline
    Super + m & Monocle layout. \\
    \hline
    Super + Shift + t & Bottom stack layout. \\
    \hline
    Super + Shift + m & Master center layout. \\
    \hline
    Super + bracketleft & Switch to the last layout. \\
    \hline
    Super + Shift + bracketleft & Toggle floating. \\
    \hline
    Super + Ctrl + comma & Cycle through layouts. \\
    \hline
    Super + Ctrl + period & Inverse cycle through layouts. \\
    \hline
    Super + Ctrl + s & Toggle sticky. \\
    \hline
    Super + 1-9 & Switch to tag 1-9. \\
    \hline
    Super + Shift + 1-9 & Send window to tag 1-9. \\
    \hline
    Super + Ctrl + 1-9 & Show tag 1-9. \\
    \hline
    Super + Ctrl + Shift + 1-9 & Add window to tag 1-9. \\
    \hline
    Super + comma & Focus monitor. \\
    \hline
    Super + period & Focus monitor. \\
    \hline
    Super + Shift + comma & Tag monitor. \\
    \hline
    Super + Shift + period & Tag monitor. \\
    \hline
    Super + Ctrl + f & Toggle the ability to focus floating windows. \\
    \hline
    Super + Shift + q & Quit window manager. \\
    \hline

\end{longtable}
