\section{SXHKD}

\begin{longtable}{|c|c|}

    \caption{SXKHD keybindings}  \\

    \hline
    Key & Action \\
    \hline
    \hline

    \endhead
    \label{tab:sxkhd-keybindings}

    super + Return & Open terminal. \\
    \hline
    super + alt + t & Toggle timer \\
    \hline
    super + n  & Open file manager \\
    \hline
    super + ctrl + b & Open system monitor. \\
    \hline
    super + ctrl + w & Open network manager. \\
    \hline
    super + e & Open text editor. \\
    \hline
    super + d & Open selection menu. \\
    \hline
    super + p & Select password to copy into clipboard. \\
    \hline
    super + equal & Open calculator. \\
    \hline
    super + L & Lock screen. \\
    \hline
    super + s & Shutdown/reboot/sleep/hibernate/exist. \\
    \hline
    super + w & Open browser \\
    \hline
    super + control + c & Open clipboard history. \\
    \hline
    alt + space & Change language. \\
    \hline
    super + alt + p & Open volume manager. \\
    \hline
    Print & Take screenshot of screen into clipboard. \\
    \hline
    Print + super & Take screenshot of screen and save. \\
    \hline
    Print + shift & Take screenshot of focused into clipboard. \\
    \hline
    Print + shift + super & Take screenshot of focused and save. \\
    \hline
    Print + control & Select window to screenshot into clipboard. \\
    \hline
    Print + control + super & Select window to screenshot and save. \\
    \hline
    super + r & Record screen. \\
    \hline
    super + R & Toggle showing screen keys. \\
    \hline
    super + alt + r & Open camera. \\
    \hline
    super + z & Toggle keyboard led. \\
    \hline

\end{longtable}
